Bandwidth-Aware Reconfigurable Memory Design with Hybrid Memory Technologies

### 2011-04-06 trunk/paper.tex

<pseudocode>

@@

Memory reconfiguration relies on accurate predictions of demand bandwidth of a
workload in response to the dynamically varying application characteristics.
Conventional last value or table based predictors can model neither long range
patterns of an application nor patterns with variable lengths. In this work, we
employ a statistical predictor to support for the BAROM design. The basic idea
of the predictor is borrowed from language modeling~\cite{smoothing-tech}.

>>>>

<pseudocode>
if (si < stotali/2): 
   if (si+1 <= stotali-si):
      si.5 = stotali-si;

else:
   si+1 = ...;

@@

Memory reconfiguration relies on accurate predictions of demand bandwidth of a
workload in response to the dynamically varying application characteristics.
Conventional last value or table based predictors can model neither long range
patterns of an application nor patterns with variable lengths. In this work, we
employ a statistical predictor to support for the BAROM design. The basic idea
of the predictor is borrowed from the n-Gram models, which are typically used by
speech and natural language processing~\cite{smoothing-tech}. The n-Gram models
are usually formulated as a probability distribution $p(s)$ over a strings $s$,
and attemp to reflect how frequently the string occurs as a sentense. Prediction
on a reasonable combination of strings is then generated based on the
probability distribution. Our predictor employs the same basic idea, but
simplifies the model for performance considerations. In our model, each demand
bandwidth sample abtained in a time interval is a string, and a given length
(the ``order'') of samples is stored in a table as a pattern. We calculate the
probability of each pattern at each time interval, and predict the demand
bandwidth for the next time interval based on the probabilities.

Figure~\ref{fig:predictor} shows the hardware components of our prediction
engine, which includes a pattern look-up-table, a probability vector, and a set
of counters.
